---
title: "R Descriptive Replication: Hidden Benefits of Abstaining from Control"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup}
input_dir <- dirname(knitr::current_input(dir = TRUE))
repo_root <- normalizePath(file.path(input_dir, "..", ".."))
knitr::opts_knit$set(root.dir = repo_root)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(dplyr)
library(haven)
library(knitr)
```

This document is an independent R-based descriptive check for Burdin, Halliday,
and Landini (2018). It is intended to complement the original Stata replication
workflow in `code/stata/run_all.do`, not replace it.

```{r load-data}
data_path <- file.path("data", "processed", "merged_treatment_control.dta")
df <- read_dta(data_path)

agents <- df %>%
  filter(playedrolea == 1) %>%
  mutate(
    treatment_label = case_when(
      treatment == 1 ~ "C10",
      treatment == 2 ~ "TP10",
      TRUE ~ as.character(treatment)
    ),
    diff_no_control_control = transferunbounded - transferbounded,
    published_category = case_when(
      controlpos == 1 ~ "Negative",
      controlneutral == 1 ~ "Neutral",
      controlneg == 1 ~ "Positive",
      TRUE ~ NA_character_
    )
  )
```

## Sample Sizes

```{r sample-sizes}
agents %>%
  count(treatment_label, name = "agents") %>%
  kable()
```

## Table 1 Descriptive Cells

```{r table-1-descriptives}
summarize_transfer <- function(data, variable) {
  x <- data[[variable]]
  tibble(
    mean = mean(x, na.rm = TRUE),
    sd = sd(x, na.rm = TRUE),
    q1 = as.numeric(quantile(x, 0.25, na.rm = TRUE)),
    median = median(x, na.rm = TRUE),
    q3 = as.numeric(quantile(x, 0.75, na.rm = TRUE))
  )
}

table1_control <- agents %>%
  group_by(treatment_label) %>%
  group_modify(~ summarize_transfer(.x, "transferbounded")) %>%
  mutate(variable = "Control transfer")

table1_no_control <- agents %>%
  group_by(treatment_label) %>%
  group_modify(~ summarize_transfer(.x, "transferunbounded")) %>%
  mutate(variable = "No-control transfer")

bind_rows(table1_control, table1_no_control) %>%
  select(treatment_label, variable, mean, sd, q1, median, q3) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2))) %>%
  kable()
```

```{r table-1-differences}
agents %>%
  group_by(treatment_label) %>%
  summarize(
    mean_difference = mean(diff_no_control_control, na.rm = TRUE),
    sd_difference = sd(diff_no_control_control, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2))) %>%
  kable()
```

## Table 2 Response Categories

Published Table 2 reports response categories from the perspective of response
to control abstinence. The Stata data labels `controlpos` and `controlneg` from
the perspective of response to control, so the non-neutral labels are reversed
when matching the published table.

```{r table-2-categories}
agents %>%
  filter(!is.na(published_category)) %>%
  group_by(treatment_label, published_category) %>%
  summarize(
    n = n(),
    share = n() / nrow(cur_data_all()),
    mean_control_transfer = mean(transferbounded, na.rm = TRUE),
    sd_control_transfer = sd(transferbounded, na.rm = TRUE),
    .groups = "drop_last"
  ) %>%
  mutate(
    treatment_n = sum(n),
    share = n / treatment_n,
    share_percent = 100 * share
  ) %>%
  ungroup() %>%
  select(
    treatment_label,
    published_category,
    n,
    share_percent,
    mean_control_transfer,
    sd_control_transfer
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2))) %>%
  kable()
```

## Table 3 GCOS Means

```{r table-3-gcos}
agents %>%
  group_by(treatment_label) %>%
  summarize(
    autonomy = mean(autonomy, na.rm = TRUE),
    impersonal = mean(impersonal, na.rm = TRUE),
    control = mean(controlpref, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2))) %>%
  kable()
```

## Result 6 Control Choice Proportions

```{r result-6-control-choice}
bind_rows(
  df %>%
    filter(playedroleb == 1, treatment == 1) %>%
    summarize(
      group = "C10 principals",
      observations = n(),
      share_choosing_control = mean(transferisbounded, na.rm = TRUE)
    ),
  df %>%
    filter(playedrolec == 1, treatment == 2) %>%
    summarize(
      group = "TP10 third parties",
      observations = n(),
      share_choosing_control = mean(transferisbounded, na.rm = TRUE)
    )
) %>%
  mutate(share_choosing_control = round(100 * share_choosing_control, 2)) %>%
  kable()
```

## Next Steps

The next R pass should add:

- Bootstrap confidence intervals for Table 1 with matched seeds and conventions.
- Wilcoxon signed-rank, Mann-Whitney, Fisher exact, and Kruskal-Wallis tests.
- Table 4 regression estimates and marginal effects.
- Rendered figures corresponding to Figs. 1 and 2.
