---
title: "R Replication Supplement: Hidden Benefits of Abstaining from Control"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup}
input_dir <- dirname(knitr::current_input(dir = TRUE))
repo_root <- normalizePath(file.path(input_dir, "..", ".."))
knitr::opts_knit$set(root.dir = repo_root)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(boot)
library(dplyr)
library(ggplot2)
library(haven)
library(knitr)
library(lmtest)
library(sandwich)

r_table_dir <- file.path(repo_root, "results", "tables", "r")
r_figure_dir <- file.path(repo_root, "results", "figures", "r")
dir.create(r_table_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(r_figure_dir, recursive = TRUE, showWarnings = FALSE)
```

This document is an independent R-based replication supplement for Burdin,
Halliday, and Landini (2018). It is intended to complement the original Stata
workflow in `code/stata/run_all.do`, not replace it. The original Stata script
remains the canonical analysis file until we can execute it and compare every
output.

The R checks below reproduce the main descriptive tables, nonparametric tests,
CDF figures, and an R version of the Table 4 regression/marginal-effect
estimates. Stata-specific details such as exact bootstrap conventions and
`mfx` standard errors should still be compared against a Stata run.

## Replication Status

```{r replication-status}
replication_status <- tibble::tribble(
  ~item, ~current_r_status, ~stata_status, ~note,
  "Figures 1 and 2", "R renders CDFs from included data", "Pending", "Visual comparison to article still needed",
  "Table 1", "Means, SDs, quartiles, and mean differences match", "Pending", "R bootstrap is an independent check, not exact Stata RNG parity",
  "Table 2", "Shares and control-transfer means match after label-orientation check", "Pending", "Published labels are response to control abstinence",
  "Table 3", "GCOS means match", "Pending", "R t-tests and Mann-Whitney checks included",
  "Table 4", "Point-estimate convention reproduced closely", "Pending", "Stata `mfx compute` standard errors and stars still need canonical check",
  "Result 6", "Control-choice proportions and tests computed", "Pending", "Published percentages match up to rounding convention",
  "Appendix A1", "Subject/earnings cells and questionnaire demographics partly checked", "Pending", "C10 demographics close but not exact; TP10 session count may be typo or convention"
)
write.csv(replication_status, file.path(r_table_dir, "replication_status.csv"), row.names = FALSE)
replication_status %>%
  kable()
```

The tables and figures generated by this report are also written to
`results/tables/r/` and `results/figures/r/` for easier review.

```{r helpers}
fmt_num <- function(x, digits = 2) {
  ifelse(is.na(x), NA_character_, formatC(x, format = "f", digits = digits))
}

fmt_p <- function(x) {
  ifelse(
    is.na(x),
    NA_character_,
    ifelse(x < 0.001, "<0.001", formatC(x, format = "f", digits = 3))
  )
}

stars <- function(p) {
  case_when(
    is.na(p) ~ "",
    p < 0.01 ~ "***",
    p < 0.05 ~ "**",
    p < 0.10 ~ "*",
    TRUE ~ ""
  )
}

fmt_est <- function(estimate, p_value, digits = 3) {
  paste0(fmt_num(estimate, digits), stars(p_value))
}

bootstrap_mean_ci <- function(x, reps = 100000, seed = 17884, level = 0.95) {
  x <- x[!is.na(x)]
  set.seed(seed)
  means <- replicate(reps, mean(sample(x, length(x), replace = TRUE)))
  estimate <- mean(x)
  se <- sd(means)
  alpha <- 1 - level
  tibble(
    estimate = estimate,
    se = se,
    normal_lower = estimate - qnorm(1 - alpha / 2) * se,
    normal_upper = estimate + qnorm(1 - alpha / 2) * se,
    percentile_lower = unname(quantile(means, alpha / 2)),
    percentile_upper = unname(quantile(means, 1 - alpha / 2)),
    reps = reps
  )
}

tidy_wilcox <- function(test, label) {
  tibble(
    check = label,
    method = test$method,
    statistic = unname(test$statistic),
    p_value = test$p.value
  )
}

tidy_htest <- function(test, label) {
  tibble(
    check = label,
    method = test$method,
    statistic = unname(test$statistic),
    p_value = test$p.value
  )
}

match_note <- function(observed, target, digits = 2) {
  ifelse(
    round(observed, digits) == target,
    "matches after rounding",
    paste0("differs: observed ", fmt_num(observed, digits), ", target ", fmt_num(target, digits))
  )
}
```

```{r load-data}
data_path <- file.path("data", "processed", "merged_treatment_control.dta")
df <- read_dta(data_path)

df <- df %>%
  mutate(
    treatment_label = case_when(
      treatment == 1 ~ "C10",
      treatment == 2 ~ "TP10",
      TRUE ~ as.character(treatment)
    )
  )

agents <- df %>%
  filter(playedrolea == 1) %>%
  mutate(
    diff_no_control_control = transferunbounded - transferbounded,
    published_category = case_when(
      controlpos == 1 ~ "Negative",
      controlneutral == 1 ~ "Neutral",
      controlneg == 1 ~ "Positive",
      TRUE ~ NA_character_
    ),
    published_category = factor(
      published_category,
      levels = c("Negative", "Neutral", "Positive")
    )
  )

appendix_demographics_path <- file.path(
  "docs",
  "audit",
  "appendix_a1_demographics_audit.csv"
)

appendix_demographics <- if (file.exists(appendix_demographics_path)) {
  read.csv(appendix_demographics_path, stringsAsFactors = FALSE)
} else {
  NULL
}
```

## Sample Sizes

```{r sample-sizes}
sample_sizes <- agents %>%
  count(treatment_label, name = "agents") %>%
  arrange(treatment_label)
write.csv(sample_sizes, file.path(r_table_dir, "sample_sizes.csv"), row.names = FALSE)
sample_sizes %>%
  kable()
```

```{r published-target-checks}
target_checks <- bind_rows(
  agents %>%
    group_by(treatment_label) %>%
    summarize(
      observed = n(),
      .groups = "drop"
    ) %>%
    mutate(
      check = paste0("Agent sample size: ", treatment_label),
      target = c(C10 = 38, TP10 = 53)[treatment_label],
      status = ifelse(observed == target, "matches", "differs")
    ) %>%
    select(check, observed, target, status),
  agents %>%
    group_by(treatment_label) %>%
    summarize(
      observed = mean(diff_no_control_control, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      check = paste0("Table 1 mean xNC - xC: ", treatment_label),
      target = c(C10 = 3.76, TP10 = -5.13)[treatment_label],
      status = match_note(observed, target)
    ) %>%
    select(check, observed, target, status),
  agents %>%
    group_by(treatment_label) %>%
    summarize(
      observed = mean(autonomy, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      check = paste0("Table 3 autonomy mean: ", treatment_label),
      target = c(C10 = 73.53, TP10 = 71.30)[treatment_label],
      status = match_note(observed, target)
    ) %>%
    select(check, observed, target, status)
)

target_checks_export <- target_checks %>%
  mutate(
    observed = round(observed, 2),
    target = round(target, 2)
  )
write.csv(target_checks_export, file.path(r_table_dir, "published_target_checks.csv"), row.names = FALSE)
target_checks_export %>%
  kable()
```

## Figures 1 and 2

The figures below reproduce the empirical CDFs for control and no-control
transfers among agents.

```{r cdf-data}
cdf_data <- agents %>%
  select(treatment_label, transferbounded, transferunbounded) %>%
  tidyr::pivot_longer(
    cols = c(transferbounded, transferunbounded),
    names_to = "condition",
    values_to = "transfer"
  ) %>%
  mutate(
    condition = recode(
      condition,
      transferbounded = "Control",
      transferunbounded = "No control"
    )
  )
```

```{r cdf-c10, fig.width=7, fig.height=4}
p_cdf_c10 <- cdf_data %>%
  filter(treatment_label == "C10") %>%
  ggplot(aes(x = transfer, color = condition, linetype = condition)) +
  stat_ecdf(geom = "step", linewidth = 0.9) +
  scale_x_continuous(breaks = seq(0, 60, 10)) +
  labs(
    title = "Cumulative distributions of transfers for C10",
    subtitle = "Agents only, n = 38",
    x = "Transfer (x)",
    y = "Cumulative probability",
    color = NULL,
    linetype = NULL
  ) +
  theme_minimal(base_size = 12)
p_cdf_c10
ggsave(file.path(r_figure_dir, "figure_1_cdf_c10.png"), p_cdf_c10, width = 7, height = 4, dpi = 300)
```

```{r cdf-tp10, fig.width=7, fig.height=4}
p_cdf_tp10 <- cdf_data %>%
  filter(treatment_label == "TP10") %>%
  ggplot(aes(x = transfer, color = condition, linetype = condition)) +
  stat_ecdf(geom = "step", linewidth = 0.9) +
  scale_x_continuous(breaks = seq(0, 60, 10)) +
  labs(
    title = "Cumulative distributions of transfers for TP10",
    subtitle = "Agents only, n = 53",
    x = "Transfer (x)",
    y = "Cumulative probability",
    color = NULL,
    linetype = NULL
  ) +
  theme_minimal(base_size = 12)
p_cdf_tp10
ggsave(file.path(r_figure_dir, "figure_2_cdf_tp10.png"), p_cdf_tp10, width = 7, height = 4, dpi = 300)
```

## Table 1

```{r table-1-descriptives}
summarize_transfer <- function(data, variable) {
  x <- data[[variable]]
  tibble(
    mean = mean(x, na.rm = TRUE),
    sd = sd(x, na.rm = TRUE),
    q1 = as.numeric(quantile(x, 0.25, na.rm = TRUE)),
    median = median(x, na.rm = TRUE),
    q3 = as.numeric(quantile(x, 0.75, na.rm = TRUE))
  )
}

table1_control <- agents %>%
  group_by(treatment_label) %>%
  group_modify(~ summarize_transfer(.x, "transferbounded")) %>%
  mutate(variable = "Control transfer")

table1_no_control <- agents %>%
  group_by(treatment_label) %>%
  group_modify(~ summarize_transfer(.x, "transferunbounded")) %>%
  mutate(variable = "No-control transfer")

table1_descriptives <- bind_rows(table1_control, table1_no_control) %>%
  select(treatment_label, variable, mean, sd, q1, median, q3) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
write.csv(table1_descriptives, file.path(r_table_dir, "table1_descriptives.csv"), row.names = FALSE)
table1_descriptives %>%
  kable()
```

```{r table-1-differences}
table1_differences <- agents %>%
  group_by(treatment_label) %>%
  summarize(
    mean_difference = mean(diff_no_control_control, na.rm = TRUE),
    sd_difference = sd(diff_no_control_control, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
write.csv(table1_differences, file.path(r_table_dir, "table1_differences.csv"), row.names = FALSE)
table1_differences %>%
  kable()
```

### Bootstrap Confidence Intervals

The original Stata file uses `bootstrap` with 100,000 repetitions and seed
17884. R and Stata use different random-number generators, so the intervals
below should be treated as an independent check rather than a byte-for-byte
match to Stata. The normal intervals closely track the published Table 1
intervals.

```{r table-1-bootstrap}
table1_bootstrap <- agents %>%
  group_by(treatment_label) %>%
  group_modify(~ bootstrap_mean_ci(.x$diff_no_control_control)) %>%
  ungroup() %>%
  transmute(
    treatment_label,
    mean_difference = estimate,
    normal_95_ci = paste0("[", fmt_num(normal_lower), ", ", fmt_num(normal_upper), "]"),
    percentile_95_ci = paste0("[", fmt_num(percentile_lower), ", ", fmt_num(percentile_upper), "]"),
    reps
  )
write.csv(table1_bootstrap, file.path(r_table_dir, "table1_bootstrap_ci.csv"), row.names = FALSE)
table1_bootstrap %>%
  kable()
```

## Nonparametric Tests

These tests mirror the signed-rank, rank-sum, Kruskal-Wallis, and Fisher exact
checks in `code/stata/master_do_file.do`.

```{r nonparametric-tests}
c10 <- agents %>% filter(treatment_label == "C10")
tp10 <- agents %>% filter(treatment_label == "TP10")

test_results <- bind_rows(
  tidy_wilcox(
    wilcox.test(c10$transferbounded, c10$transferubx, paired = TRUE, exact = FALSE),
    "Result 1: C10 control vs modified no-control transfer"
  ),
  tidy_wilcox(
    wilcox.test(c10$transferbounded, c10$transferunbounded, paired = TRUE, exact = FALSE),
    "Result 2: C10 control vs no-control transfer"
  ),
  tidy_wilcox(
    wilcox.test(tp10$transferbounded, tp10$transferunbounded, paired = TRUE, exact = FALSE),
    "Result 4: TP10 control vs no-control transfer"
  ),
  tidy_wilcox(
    wilcox.test(tp10$transferbounded, tp10$transferubx, paired = TRUE, exact = FALSE),
    "Result 3: TP10 control vs modified no-control transfer"
  ),
  tidy_wilcox(
    wilcox.test(transferunbounded ~ treatment_label, data = agents, exact = FALSE),
    "C10 vs TP10 no-control transfer"
  ),
  tidy_wilcox(
    wilcox.test(transferbounded ~ treatment_label, data = agents, exact = FALSE),
    "C10 vs TP10 control transfer"
  ),
  tidy_htest(
    kruskal.test(transferunbounded ~ treatment_label, data = agents),
    "Kruskal-Wallis: no-control transfer by treatment"
  ),
  tidy_htest(
    kruskal.test(transferbounded ~ treatment_label, data = agents),
    "Kruskal-Wallis: control transfer by treatment"
  )
)

test_results_export <- test_results %>%
  mutate(
    statistic = round(statistic, 3),
    p_value = fmt_p(p_value)
  )
write.csv(test_results_export, file.path(r_table_dir, "nonparametric_tests.csv"), row.names = FALSE)
test_results_export %>%
  kable()
```

## Table 2 Response Categories

Published Table 2 reports response categories from the perspective of response
to control abstinence. The Stata data labels `controlpos` and `controlneg` from
the perspective of response to control, so the non-neutral labels are reversed
when matching the published table.

```{r table-2-categories}
table2_categories <- agents %>%
  filter(!is.na(published_category)) %>%
  count(treatment_label, published_category, name = "n") %>%
  left_join(
    agents %>%
      group_by(treatment_label, published_category) %>%
      summarize(
        mean_control_transfer = mean(transferbounded, na.rm = TRUE),
        sd_control_transfer = sd(transferbounded, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("treatment_label", "published_category")
  ) %>%
  group_by(treatment_label) %>%
  mutate(share_percent = 100 * n / sum(n)) %>%
  ungroup() %>%
  select(
    treatment_label,
    published_category,
    n,
    share_percent,
    mean_control_transfer,
    sd_control_transfer
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
write.csv(table2_categories, file.path(r_table_dir, "table2_response_categories.csv"), row.names = FALSE)
table2_categories %>%
  kable()
```

```{r table-2-fisher}
fisher_results <- bind_rows(
  tidy_htest(fisher.test(table(agents$controlpos, agents$treatment_label)), "Published negative category"),
  tidy_htest(fisher.test(table(agents$controlneutral, agents$treatment_label)), "Published neutral category"),
  tidy_htest(fisher.test(table(agents$controlneg, agents$treatment_label)), "Published positive category")
)

fisher_results_export <- fisher_results %>%
  mutate(
    statistic = NA,
    p_value = fmt_p(p_value)
  )
write.csv(fisher_results_export, file.path(r_table_dir, "table2_fisher_tests.csv"), row.names = FALSE)
fisher_results_export %>%
  kable()
```

## Table 3 GCOS Means and Tests

```{r table-3-gcos}
table3_gcos <- agents %>%
  group_by(treatment_label) %>%
  summarize(
    autonomy = mean(autonomy, na.rm = TRUE),
    impersonal = mean(impersonal, na.rm = TRUE),
    control = mean(controlpref, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
write.csv(table3_gcos, file.path(r_table_dir, "table3_gcos_means.csv"), row.names = FALSE)
table3_gcos %>%
  kable()
```

```{r table-3-tests}
gcos_tests <- bind_rows(
  tidy_htest(t.test(autonomy ~ treatment_label, data = agents), "Autonomy t-test"),
  tidy_htest(t.test(impersonal ~ treatment_label, data = agents), "Impersonal t-test"),
  tidy_htest(t.test(controlpref ~ treatment_label, data = agents), "Control t-test"),
  tidy_wilcox(wilcox.test(autonomy ~ treatment_label, data = agents, exact = FALSE), "Autonomy Mann-Whitney"),
  tidy_wilcox(wilcox.test(impersonal ~ treatment_label, data = agents, exact = FALSE), "Impersonal Mann-Whitney"),
  tidy_wilcox(wilcox.test(controlpref ~ treatment_label, data = agents, exact = FALSE), "Control Mann-Whitney")
)

gcos_tests_export <- gcos_tests %>%
  mutate(
    statistic = round(statistic, 3),
    p_value = fmt_p(p_value)
  )
write.csv(gcos_tests_export, file.path(r_table_dir, "table3_gcos_tests.csv"), row.names = FALSE)
gcos_tests_export %>%
  kable()
```

## Table 4 Regression Check

The first two columns below are OLS coefficients with HC3 robust p-values, as in
the Stata script. The remaining columns are logit marginal effects evaluated at
sample means. For the binary TP10 indicator, the value is the discrete change
from C10 to TP10 at the means of the standardized GCOS scales. This convention
matches the published point estimates closely; the standard errors and stars
should still be checked against Stata's `mfx compute` output.

```{r table-4-functions}
ols_cell <- function(model, term) {
  ct <- coeftest(model, vcov. = vcovHC(model, type = "HC3"))
  tibble(
    term = term,
    estimate = unname(ct[term, "Estimate"]),
    p_value = unname(ct[term, "Pr(>|t|)"])
  )
}

logit_mfx_at_means <- function(data, outcome, term) {
  model <- glm(
    reformulate(c("treatdum", "stauto", "stimp", "stcont"), response = outcome),
    data = data,
    family = binomial()
  )

  means <- data.frame(
    treatdum = mean(data$treatdum, na.rm = TRUE),
    stauto = mean(data$stauto, na.rm = TRUE),
    stimp = mean(data$stimp, na.rm = TRUE),
    stcont = mean(data$stcont, na.rm = TRUE)
  )

  if (term == "treatdum") {
    means0 <- means
    means1 <- means
    means0$treatdum <- 0
    means1$treatdum <- 1
    estimate <- predict(model, means1, type = "response") -
      predict(model, means0, type = "response")
  } else {
    p_at_means <- predict(model, means, type = "response")
    estimate <- coef(model)[term] * p_at_means * (1 - p_at_means)
  }

  ct <- coeftest(model, vcov. = vcovHC(model, type = "HC0"))
  tibble(
    term = term,
    estimate = unname(estimate),
    p_value = unname(ct[term, "Pr(>|z|)"])
  )
}

terms <- c("treatdum", "stauto", "stimp", "stcont")
term_labels <- c(
  treatdum = "D: TP10 treatment = 1",
  stauto = "Standardized autonomy scale",
  stimp = "Standardized impersonal scale",
  stcont = "Standardized control scale"
)

ols_xnc <- lm(transferunbounded ~ treatdum + stauto + stimp + stcont, data = agents)
ols_diff <- lm(diff_no_control_control ~ treatdum + stauto + stimp + stcont, data = agents)

table4 <- tibble(term = terms, label = unname(term_labels[terms])) %>%
  rowwise() %>%
  mutate(
    xNC = list(ols_cell(ols_xnc, term)),
    `xNC - xC` = list(ols_cell(ols_diff, term)),
    Negative = list(logit_mfx_at_means(agents, "controlpos", term)),
    Neutral = list(logit_mfx_at_means(agents, "controlneutral", term)),
    Positive = list(logit_mfx_at_means(agents, "controlneg", term))
  ) %>%
  ungroup()

table4_export <- table4 %>%
  rowwise() %>%
  transmute(
    variable = label,
    xNC = fmt_est(xNC$estimate, xNC$p_value),
    `xNC - xC` = fmt_est(`xNC - xC`$estimate, `xNC - xC`$p_value),
    Negative = fmt_est(Negative$estimate, Negative$p_value),
    Neutral = fmt_est(Neutral$estimate, Neutral$p_value),
    Positive = fmt_est(Positive$estimate, Positive$p_value)
  ) %>%
  ungroup()
write.csv(table4_export, file.path(r_table_dir, "table4_regression_check.csv"), row.names = FALSE)
table4_export %>%
  kable()
```

## Result 6 Control Choice Proportions

```{r result-6-control-choice}
control_choice <- bind_rows(
  df %>%
    filter(playedroleb == 1, treatment == 1) %>%
    transmute(treatment_label, controller = transferisbounded, group = "C10 principals"),
  df %>%
    filter(playedrolec == 1, treatment == 2) %>%
    transmute(treatment_label, controller = transferisbounded, group = "TP10 third parties")
)

result6_proportions <- control_choice %>%
  group_by(group) %>%
  summarize(
    observations = n(),
    share_choosing_control = 100 * mean(controller, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(share_choosing_control = round(share_choosing_control, 2))
write.csv(result6_proportions, file.path(r_table_dir, "result6_control_choice_proportions.csv"), row.names = FALSE)
result6_proportions %>%
  kable()
```

```{r result-6-tests}
result6_tests <- bind_rows(
  tidy_htest(fisher.test(table(control_choice$controller, control_choice$treatment_label)), "Fisher exact: control choice by treatment"),
  tidy_wilcox(wilcox.test(controller ~ treatment_label, data = control_choice, exact = FALSE), "Mann-Whitney: control choice by treatment")
)

result6_tests_export <- result6_tests %>%
  mutate(
    statistic = round(statistic, 3),
    p_value = fmt_p(p_value)
  )
write.csv(result6_tests_export, file.path(r_table_dir, "result6_tests.csv"), row.names = FALSE)
result6_tests_export %>%
  kable()
```

```{r result-6-bootstrap}
set.seed(80023)
c10_controller <- control_choice$controller[control_choice$treatment_label == "C10"]
tp10_controller <- control_choice$controller[control_choice$treatment_label == "TP10"]
result6_estimate <- mean(tp10_controller) - mean(c10_controller)
result6_boot <- replicate(
  100000,
  mean(sample(tp10_controller, length(tp10_controller), replace = TRUE)) -
    mean(sample(c10_controller, length(c10_controller), replace = TRUE))
)

result6_bootstrap <- tibble(
  estimate = result6_estimate,
  normal_95_ci = paste0(
    "[",
    fmt_num(result6_estimate - qnorm(0.975) * sd(result6_boot)),
    ", ",
    fmt_num(result6_estimate + qnorm(0.975) * sd(result6_boot)),
    "]"
  ),
  percentile_95_ci = paste0(
    "[",
    fmt_num(unname(quantile(result6_boot, 0.025))),
    ", ",
    fmt_num(unname(quantile(result6_boot, 0.975))),
    "]"
  )
)
write.csv(result6_bootstrap, file.path(r_table_dir, "result6_bootstrap_ci.csv"), row.names = FALSE)
result6_bootstrap %>%
  kable()
```

## Appendix A1 Checks

Several Appendix A1 cells are directly checkable from the consolidated data.
The TP10 subject count matches the paper. The consolidated `sessionid` variable
has eight distinct TP10 values whereas the paper reports seven sessions. The raw
session audit shows that all non-crash zTree exports are represented in the
cleaned data, so this is best treated as a session-definition question or a
possible article typo rather than a substantive missing-data problem.

```{r appendix-a1-partial}
appendix_a1_partial <- df %>%
  group_by(treatment_label) %>%
  summarize(
    sessions_in_consolidated_data = n_distinct(sessionid),
    subjects = n(),
    agent_earnings = mean(finalearnings[playedrolea == 1], na.rm = TRUE),
    agent_earnings_sd = sd(finalearnings[playedrolea == 1], na.rm = TRUE),
    principal_earnings = mean(finalearnings[playedroleb == 1], na.rm = TRUE),
    principal_earnings_sd = sd(finalearnings[playedroleb == 1], na.rm = TRUE),
    third_party_earnings = mean(finalearnings[playedrolec == 1], na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
write.csv(appendix_a1_partial, file.path(r_table_dir, "appendix_a1_partial_checks.csv"), row.names = FALSE)
appendix_a1_partial %>%
  kable()
```

### Questionnaire Demographics

The demographic cells in Appendix A1 appear to come from questionnaire
respondents rather than from every zTree subject. The audit below is aggregate
only and does not export row-level demographics, majors, birthdates, or free
text.

```{r appendix-a1-demographics}
if (!is.null(appendix_demographics)) {
  appendix_demographics_export <- appendix_demographics %>%
    transmute(
      treatment,
      demographic_rows,
      female_count_from_text,
      female_share_from_dummy = round(female_share_from_dummy, 4),
      paper_female_share,
      female_share_rounded_matches_paper,
      age_mean = round(age_mean, 4),
      paper_age_mean,
      age_mean_rounded_matches_paper,
      age_sd = round(age_sd, 4),
      paper_age_sd,
      age_sd_rounded_matches_paper,
      note
    )
  write.csv(appendix_demographics_export, file.path(r_table_dir, "appendix_a1_demographics_audit.csv"), row.names = FALSE)
  appendix_demographics_export %>%
    kable()
} else {
  cat("Demographics audit CSV not found.")
}
```

## Remaining Work

- Run the original Stata workflow and compare generated outputs to this R
  supplement.
- Check Stata's exact `bootstrap` and `mfx compute` standard-error conventions.
- Add a public-facing `results/` export only after Stata and R outputs are
  reconciled.
- Resolve the small Appendix A1 provenance notes: C10 demographics are close but
  not exact, and the TP10 seven-session count is probably a typo or counting
  convention unless lab records show otherwise.
